\section{Group Information}
\subsection{Hoàng Đôn Thiện Hòa (23125035) - Leader}
\begin{itemize}
    \item  Management: Planning timeline, plans for the project.
    \item Coding Process:
    \begin{itemize}
        \item Work on the Graph logic part (ShortestPath, Kruskal, MST).
        \item Support work on Graph visualization.
        \item Support work on other parts.
        \item Fix bugs, control and optimize the code.
        \item Finalize and complete the project.

    \end{itemize}
    => Contribution Percentage: 23\%
\end{itemize}

\subsection{Nguyễn Lê Quốc Huy (24125100)}
\begin{itemize}
    \item Coding Process    
    \begin{itemize}
        \item Work on Graph Visualization.
        \item Participate in building program structure (design OOP).
        \item Work on coding and design common GUI 
        \item Code UI Controller.
        \item Work on LinearHashTable (logic part).
        \item Support work on AVL Tree (visualization and effect).
        \item Support work on program effect.
    \end{itemize}
    => Contribution Percentage: 27\%
\end{itemize}

\subsection{Lê Đức Thịnh (24125045)}
\begin{itemize}
    \item Coding Process    
    \begin{itemize}
        \item Work on logic for AVL Tree (Create, insert, move).
        \item Support work on LinearHashTable (visualization, functions: create, insert, remove, update).
        \item Highlight code for Linear Hash Table.
        \item Design the texture for buttons and relevant images (Dark/Light theme).
        \item Work on MenuTab for changing data structures.
    \end{itemize}
    => Contribution Percentage: 26\%
\end{itemize}

\subsection{Lê Văn Vĩ (24125050)}
\begin{itemize}
    \item Coding Process    
    \begin{itemize}
        \item + Working on logic and visualization for the Singly Linked List.
        \item Support working on the Command List.
    \end{itemize}
    => Contribution Percentage: 24\%
\end{itemize}